Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Assigned the retro gender, age, ethnicity, employment and diagnosis graphs to objects

dat.retro %>% 
  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")

@@

dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000))

@@

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Mental health diagnosis",
       y = "N participants") +
  ylim(0, 20000) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank())

@@

>>>>

retro_gender_plot <- dat.retro %>% 
  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")

@@

retro_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000))

@@

retro_diagnosis_plot <- dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Mental health diagnosis",
       y = "N participants") +
  ylim(0, 20000) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank())

@@

#Plot Graphs together

This will plot the stacked bar charts of the gender, age, employment, ethnicity and diagnosis variables together.

```{r Plot histograms together}
